On the analytic structure of the linear response susceptibility in open systems

### 2018-05-14 AnalyticStructure_main.tex
update

The study of the localization properties of the LR functional, formerly discussed through the inspection of the response density operator, can be reformulated in terms of the 
\emph{susceptibility functional}, defined trough the operator equation  
\be\lb{SusceptibilityDef1}
\dm'(\omega) = \sop{{\cal R}}(\omega) \op\Phi(\omega) \;. 
\ee
This reformulation of the problem has the advantage of providing general information on the nature of the excitation spectrum. Results achieved in this way thus describes an intrinsic 
feature of the system under inspection and determine the properties of the LR independently from the specific choice of the perturbing field.

@@

FIRST QUESTION: The usage of the $\mu$-basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?). 
We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend this reliability of the result up to
$\omega=|\eps_p|$.

@@

The construction of the excitation operators requires the explicit sampling of the empty state subspace. Definition of the $\{\alpha\}$-basis: choose the empty eigenstates of the KS Hamiltonian as a 
basis-set to express the excited state $\ket{\phi^E_p},\bra{\tilde\chi^E_p}$ and their duals. The elements $\{\alpha\}$-basis are expressed in the $\{\mu\}$-basis: since the $\{\mu\}$-basis is finite 
dimensional so it is also the $\{\alpha\}$-basis. Excitation index becomes discrete and the basis provide a partial sampling of the continuum sector of the excitation landscape.

>>>>

The study of the localization properties of the LR functional, formerly discussed through the inspection of the response density operator, can be reformulated in terms of the 
\emph{susceptibility functional}, defined trough the operator equation  
\be\lb{SusceptibilityDef1}
\dm'(\omega) = \sop{{\cal R}}(\omega) \op\Phi(\omega) \;. 
\ee
This alternative formulation of the problem has the advantage of providing general information on the nature of the excitation spectrum. Results achieved in this way thus describes an intrinsic 
feature of the system under inspection and determine the properties of the LR independently from the specific choice of the perturbing field.

@@

FIRST QUESTION: The usage of the $\mu$-basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?). 
We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend the reliability of the result up to
$\omega=|\eps_p|$.

@@

The construction of the excitation operators requires the explicit sampling of the empty state subspace. We introduce the notion of \emph{$\{\alpha\}$-basis}: choose the empty eigenstates of the KS 
Hamiltonian as a basis-set to express the excited state $\ket{\phi^E_p},\bra{\tilde\chi^E_p}$ and their duals. Excitations are written in the basis of transitions.

COMMENT: The elements of the $\{\alpha\}$-basis are written in the (finite dimensional) $\{\mu\}$-basis. It follows that the $\{\alpha\}$-basis is finite dimensional too and has $n_\mu-n_{occ}$ degrees
of freedom. Excitation index becomes discrete and the basis provide a partial sampling of the continuum sector of the excitation landscape.
